Quality Definitions of Qualities

### 2019-11-19 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated Ao's 5 qualities

\begin{defn}
Interoperability is the ability of two or more systems or components to exchange
information and to use the information that has been exchanged
\citep{IEEEComputerDictionary1991}.
\end{defn}
\begin{defn}
The degree to which two or more systems, products or components can exchange
information and use the information that has been exchanged
\citep{ISO/IEC25010}.
\end{defn}
\begin{defn}
The capability to communicate, execute programs, and transfer data among various
functional units in a manner that requires the user to have little or no
knowledge of the unique characteristics of those units
\citep{ISO/IEC/IEEE24765}.
\end{defn}
\begin{defn}Interoperability is a characteristic of a product or system, whose
interfaces are completely understood, to work with other products or systems,
present or future, in either implementation or access, without any restrictions
\citep{AFUL2019}.
\end{defn}
\begin{defn}
\label{InteroperabilitySelected}
Interoperability is the ability of different information systems, devices and
applications (‘systems’) to access, exchange, integrate and cooperatively use
data in a coordinated manner, within and across organizational, regional and
national boundaries, to provide timely and seamless portability of information
and optimize the health of individuals and populations globally. Health data
exchange architectures, application interfaces and standards enable data to be
accessed and shared appropriately and securely across the complete spectrum of
care, within all applicable settings and with relevant stakeholders, including
by the individual \citep{HIMSS2019}.

@@

Definition \ref{InteroperabilitySelected}
rephrased: Interoperability is the ability of different information systems,
devices and applications (‘systems’) to access, exchange, integrate and
cooperatively use data in a coordinated manner, within and across
organizational, regional and national boundaries, to provide timely and seamless
portability of information.

\wss{I moved the proposed definition to the end, to match the other sections.
  Hopefully I did not change the meaning.}

@@

@@

Definition \ref{VisibilitySelected}.

@@

@@

\begin{defn}
The best definition of the productivity of a process is
\[\text{Productivity} = \dfrac{\text{Outputs produced by the
      process}}{\text{Inputs consumed by the process}}\] Defining inputs. For
the software process, providing a meaningful definition of inputs is a
nontrivial but generally workable problem. Inputs to the software process
generally comprise labor, computers, supplies, and other support facilities and
equipment. Defining outputs. The big problem in defining software productivity
is defining outputs. Here we find a defining delivered source instructions (DSI)
or lines of code as the output of the software process is totally inadequate,
and they argue that there are a number of deficiencies in using DSI. However,
most organizations doing practical productivity measurement still use DSI as
their primary metric \citep{Boehm1987}.
\end{defn}
\begin{defn}
\label{ProductivitySelected}
Productivity is the amount of output (what is produced) per unit of input
used.If we can measure the size of the software product and the effort required
to develop the product, we have:
\begin{align}
\text{productivity} = \text{size}/\text{effort}
\end{align}
Equation (1) assumes that size is the output of the software production process
and effort is the input to the process. This can be contrasted with the
viewpoint of software cost models where we use size as an independent variable
(i.e., an input) to predict effort which is treated as an output. Equation (1)
is simple to operationalize if we have a single dominant size measure, for
example, product size measured in lines of code \citep{Kitchenham2004}.
\end{defn}

@@

@@

\begin{defn}
A specification is consistent to the extent that its provisions do not conflict
with each other or with governing specifications and objectives. Specifications
require consistency in several ways \citep{Boehm1984}.
\begin{itemize}
\item Internal consistency. Items within the specification do not conflict with
each other.
\item External consistency. Items in the specification do not conflict with
external specifications or entities.
\item Traceability. Items in the specification have clear antecedents in earlier
specifications or statements of system objectives.
\end{itemize}
\end{defn}
\begin{defn}
Consistency requires that no two or more requirements in a specification
contradict each other. It is also often regarded as the case where words and
terms have the same meaning throughout the requirements specifications
(consistent use of terminology). These two views of consistency imply that
mutually exclusive statements and clashes in terminology should be avoided
\citep{ZOWGHI2003}.
\end{defn}
\begin{defn}
\label{ConsistencySelected}
Consistency: 1. the degree of uniformity, standardization, and freedom from
contradiction among the documents or parts of a system or component 2. software
attributes that provide uniform design and implementation techniques and
notations \citep{ISO/IEC/IEEE24765}.
\end{defn}

@@

Definition \ref{ConsistencySelected}.

>>>>

\begin{defn}
Interoperability is the ability of two or more systems or components to exchange
information and to use the information that has been exchanged
\citep{IEEEComputerDictionary1991}.
\end{defn}
\begin{defn}
\label{InteroperabilitySelected}
The degree to which two or more systems, products or components can exchange
information and use the information that has been exchanged
\citep{ISO/IEC25010}.
\end{defn}
\begin{defn}
The ability of a system to coexist and cooperate with other systems.
\citep{ghezzi1991fundamentals}.
\end{defn}
\begin{defn}
The capability to communicate, execute programs, and transfer data among various
functional units in a manner that requires the user to have little or no
knowledge of the unique characteristics of those units
\citep{ISO/IEC/IEEE24765}.
\end{defn}
\begin{defn}Interoperability is a characteristic of a product or system, whose
interfaces are completely understood, to work with other products or systems,
present or future, in either implementation or access, without any restrictions
\citep{AFUL2019}.
\end{defn}
\begin{defn}
Interoperability is the ability of different information systems, devices and
applications (‘systems’) to access, exchange, integrate and cooperatively use
data in a coordinated manner, within and across organizational, regional and
national boundaries, to provide timely and seamless portability of information
and optimize the health of individuals and populations globally. Health data
exchange architectures, application interfaces and standards enable data to be
accessed and shared appropriately and securely across the complete spectrum of
care, within all applicable settings and with relevant stakeholders, including
by the individual \citep{HIMSS2019}.

@@

Definition \ref{InteroperabilitySelected}
rephrased: The effort to exchange information between two or more systems,
products or components and use the information that has been exchanged.

@@

This definition is concise and also detailed enough to show the concept not only
on system, but also on products and components. Rephrased ``degree'' to
``effort'' because the latter is more measurable.

@@

Definition \ref{VisibilitySelected} rephrased: The clarity of documentation for
all of the steps and the current status of a software development process.

@@

Definition \ref{VisibilitySelected} is the only one could be found. It is
rephrased because the original one might refer to binary status - ``visible'' or
``unvisible''.

@@

\begin{defn}
A quality of the software production process, referring to its efficiency and
performance \citep{ghezzi1991fundamentals}.
\end{defn}
\begin{defn}
The best definition of the productivity of a process is
\[\text{Productivity} = \dfrac{\text{Outputs produced by the
      process}}{\text{Inputs consumed by the process}}\] Defining inputs. For
the software process, providing a meaningful definition of inputs is a
nontrivial but generally workable problem. Inputs to the software process
generally comprise labor, computers, supplies, and other support facilities and
equipment. Defining outputs. The big problem in defining software productivity
is defining outputs. Here we find a defining delivered source instructions (DSI)
or lines of code as the output of the software process is totally inadequate,
and they argue that there are a number of deficiencies in using DSI. However,
most organizations doing practical productivity measurement still use DSI as
their primary metric \citep{Boehm1987}.
\end{defn}
\begin{defn}
\label{ProductivitySelected}
Productivity is the amount of output (what is produced) per unit of input
used.If we can measure the size of the software product and the effort required
to develop the product, we have:
\begin{align}
\text{productivity} = \text{size}/\text{effort}
\end{align}
Equation (1) assumes that size is the output of the software production process
and effort is the input to the process. This can be contrasted with the
viewpoint of software cost models where we use size as an independent variable
(i.e., an input) to predict effort which is treated as an output. Equation (1)
is simple to operationalize if we have a single dominant size measure, for
example, product size measured in lines of code \citep{Kitchenham2004}.
\end{defn}

@@

It is concise and measurable.

@@

\begin{defn}
\label{ConsistencySelected}
A specification is consistent to the extent that its provisions do not conflict
with each other or with governing specifications and objectives. Specifications
require consistency in several ways \citep{Boehm1984}.
\begin{itemize}
\item Internal consistency. Items within the specification do not conflict with
each other.
\item External consistency. Items in the specification do not conflict with
external specifications or entities.
\item Traceability. Items in the specification have clear antecedents in earlier
specifications or statements of system objectives.
\end{itemize}
\end{defn}
\begin{defn}
Consistency requires that no two or more requirements in a specification
contradict each other. It is also often regarded as the case where words and
terms have the same meaning throughout the requirements specifications
(consistent use of terminology). These two views of consistency imply that
mutually exclusive statements and clashes in terminology should be avoided
\citep{ZOWGHI2003}.
\end{defn}
\begin{defn}
Consistency: 1. the degree of uniformity, standardization, and freedom from
contradiction among the documents or parts of a system or component 2. software
attributes that provide uniform design and implementation techniques and
notations \citep{ISO/IEC/IEEE24765}.
\end{defn}

@@

The first sentence of Definition \ref{ConsistencySelected}: A specification is
consistent to the extent that its provisions do not conflict with each other or
with governing specifications and objectives.
